Filling in data gaps on refugee children: Statistical imputation for missing count data

### 2023-01-24 paper.qmd
small edits, final IFMS draft version of paper

---
title: "Filling in data gaps on refugee children: Statistical imputation for missing count data"
author: Jan Beise, Yukun Pei (UNICEF); Sebastian Steinmueller (UNHCR)
abstract: UNHCR's annually published population dataset with the number of refugees and their age/sex composition by country of origin and country of asylum contained missing age data for 23 per cent of the global refugee populations at end-2021. Figures of the global proportion of refugees who are children disseminated to date used the available data only. We show that this approach likely leads to upward biased estimates of the global proportion of children due to the omission of refugee groups in the Americas and Europe with lower proportions of children. We propose a multilevel Bayesian model to create a dataset with multiple imputations of age/sex counts for country pairs with missing data, resulting in standardisation of global and regional estimates by countries of origin and regions of asylum. The estimate of the proportion of children in the global refugee population derived from the imputed dataset is 42 per cent compared to 47 per cent in the available-data figure. 
format: pdf
bibliography: references.bib
execute:
  echo: false
  warning: false
  message: false
header-includes:
    \usepackage{float}
    \usepackage{setspace}
    \onehalfspacing
toc: true
lof: true
lot: true
---

>>>>

---
title: "Filling in data gaps on refugee children: Statistical imputation for missing count data"
author: Jan Beise, Yukun Pei (UNICEF); Sebastian Steinmueller (UNHCR)
abstract: UNHCR's annually published population dataset with the number of refugees and their age/sex composition by country of origin and country of asylum contained missing age data for 23 per cent of the global refugee populations at end-2021. Figures of the global proportion of refugees who are children disseminated to date used the available data only. We show that this approach likely leads to an upward biased estimate of the global proportion of children due to the omission of refugee groups in the Americas and Europe with lower proportions of children. We propose a multilevel Bayesian model to create a dataset with multiple imputations of age/sex counts for country pairs with missing data, resulting in standardisation of global and regional estimates by countries of origin and regions of asylum. The estimate of the proportion of children in the global refugee population derived from the imputed dataset is 42 per cent compared to 47 per cent in the available-data figure. 
format: pdf
bibliography: references.bib
execute:
  echo: false
  warning: false
  message: false
header-includes:
    \usepackage{float}
    \usepackage{setspace}
    \onehalfspacing
toc: true
lof: true
lot: true
---
